Pillar 1 - Sequential Pattern Mining

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
new type of rules: not => low

### Take / not take, pass / fail / not take
```{r d_transactions TPF}
d_transactions$TPF <- expand.grid(

@@

    TPF = case_when(
      is.na(Grade)        ~ "not taken",
      Grade <  pass_grade ~ "fail",
      Grade >= pass_grade ~ "pass"
      ),

    item_TPF = paste(item, TPF, sep = "_")

@@

transactions$taken <- make_transaction(item = item   )
transactions$PF    <- make_transaction(item = item_PF)
transactions$HL    <- make_transaction(item = item_HL)
transactions$TPF   <- make_transaction(data = d_transactions$TPF, item = item_TPF)
transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )

# inspect(head(transactions, 10))
```

@@

  make_transaction, transactions, 
  make_sequence, sequences
  )
```

@@

### not take -> fail
```{r AR TPF, cache = TRUE}
AR$TPF <- transactions$TPF %>%

@@

  # Confidence and Lift
  filter(
    str_detect(rhs, "fail|pass") # only keep rhsTake for computing confidence and lift
    ) %>%
  compute_conf_lift %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "not"),
    str_detect(rhs, "fail")
    )
```

### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

@@

### take -> take
```{r SR taken, cache = TRUE}
SR <- list()

@@

### not take -> fail
```{r SR TPF, cache = TRUE}
SR$TPF <- d_transcript_cum %>%

@@

@@

    filter(
      count >= 5
      ) %>%

@@

```{r show rules}
print(AR$TPF)
print(SR$TPF)
```

>>>>

### Take / not take, pass / fail / not take
```{r d_transactions T_PF_HL}
d_transactions$T_PF_HL <- expand.grid(

@@

    TPF = case_when(
      is.na(Grade)        ~ "not",
      Grade <  pass_grade ~ "fail",
      Grade >= pass_grade ~ "pass"
      ),
    THL = case_when(
      is.na(Grade)        ~ "not",
      Grade <  high_grade ~ "low",
      Grade >= high_grade ~ "high"
      ),

    item_TPF = paste(item, TPF, sep = "_"),

    item_THL = paste(item, THL, sep = "_")

@@

transactions$taken <- make_transaction(item = item   )
transactions$PF    <- make_transaction(item = item_PF)
transactions$HL    <- make_transaction(item = item_HL)
transactions$TPF   <- make_transaction(data = d_transactions$T_PF_HL, item = item_TPF)
transactions$THL   <- make_transaction(data = d_transactions$T_PF_HL, item = item_THL)
transactions$G     <- make_transaction(data = d_transactions$G  , item = item_G  )

# inspect(head(transactions$taken, 10))
```

@@

  make_transaction, transactions, 
  make_sequence, sequences

@@

### not -> fail
```{r AR TPF, cache = TRUE}
AR$TPF <- transactions$TPF %>%

@@

  # Confidence and Lift
  filter(
    str_detect(lhs, "not"),
    str_detect(rhs, "fail|pass") # only keep rhsTake for computing confidence and lift
    ) %>%
  compute_conf_lift %>%

  # rhs must be fail, count >= 5
  filter(
    str_detect(rhs, "fail")
    )
```

### not -> low
```{r AR THL, cache = TRUE}
AR$THL <- transactions$THL %>%

  # only keep lhs is not and rhs is low or high to compute Confidence and Lift
  filter(
    str_detect(lhs, "not"),
    str_detect(rhs, "low|high")
    ) %>%
  compute_conf_lift %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(rhs, "low")
    )
```

### grade less than or equal to x -> grade less than or equal to 6

```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

@@

### take -> take
```{r SR taken, cache = TRUE, warning = FALSE}
SR <- list()

@@

### not -> fail
```{r SR TPF, cache = TRUE}
SR$TPF <- d_transcript_cum %>%

@@

### not -> low
```{r SR THL, cache = TRUE}
SR$THL <- d_transcript_cum %>%

  # rhs
  unnest(
    rhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(rhs, "high|low")
    ) %>%

  compute_rhs.support(
    data_support = d_support$PF_HL,
    type_rule    = rate.low
    ) %>%

  # lhs not, rhs low
  filter(
    str_detect(rhs, "low")
    )
```

@@

    filter(
      count >= 10
      ) %>%

@@

```{r show rules}
print(AR$THL)
print(SR$THL)
```
